Top-Down Graph-Based Neuron Reconstruction

### 2017-11-14 papers/cvpr2018/0_introduction.tex
Donglai's rough pass on sec1-3

% !TEX root =  paper.tex
\section{Introduction}

The field of connectomics is concerned with reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{kasthuri2015saturated,haehn2017scalable}. Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) have allowed researchers to produce terabytes of image data every hour~\cite{hildebrand2017whole}. It is not feasible for domain experts to manually reconstruct thousands or millions of neurons from this vast amount of image data~\cite{haehn2014design}. State-of-the-art automatic reconstruction approaches use pixel-based segmentation with convolutional neural networks (CNNs) followed by agglomeration strategies~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,lee2015recursive,ronneberger2015u}. %TODO DOUBLE CHECK REFERENCES
These \textit{bottom-up pixel-based} algorithms produce excellent results but still fall short of acceptable error rates for large volumes.

>>>>

% !TEX root =  paper.tex
\section{Introduction}
\donglai{usually, top-down means split.. but we are also bottom-up, but with different representation}
The field of connectomics is concerned with reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{kasthuri2015saturated,haehn2017scalable}. Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) have allowed researchers to produce terabytes of image data every hour~\cite{hildebrand2017whole}. It is not feasible for domain experts to manually reconstruct thousands or millions of neurons from this vast amount of image data~\cite{haehn2014design}. State-of-the-art automatic reconstruction approaches use pixel-based segmentation with convolutional neural networks (CNNs) followed by agglomeration strategies~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,lee2015recursive,ronneberger2015u}. %TODO DOUBLE CHECK REFERENCES
These \textit{bottom-up pixel-based} algorithms produce excellent results but still fall short of acceptable error rates for large volumes.

### 2017-11-14 papers/cvpr2018/2_method.tex
Donglai's rough pass on sec1-3

There are two types of errors that can occur in connectomics segmentation.
The first, called a split error, occurs when there are two segments that should have been merged. The second, called a merge error, happens when one segment should be split into two. Generally, it is much more difficult to correct merge errors than to correct split errors~\cite{parag2015properties}, which is why most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. Our method takes as input over-segmentations of EM image volumes generated by state-of-the-art connectomics reconstruction pieplines (Sec.~\ref{sec:neuroproof}). Our goal is to identify locations of split errors and merge the corresponding segments automatically.

From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with non-negative edge weights $w_e$. The nodes correspond to label segments from the segmentation with edges between segments considered for merging. Ideally, our graph has edges corresponding to all of the segments that were erroneously split. To compute this graph we generate a skeleton for every segment in the pixel-based segmentation. The skeleton is a simplified representation of the overall shape of the neurons. From this skeleton we  identify potential merge locations and produce the corresponding edges for the graph. To find actual merges we run a classification CNN to generate edge weights that correspond to probabilites of merging. We then use a multicut heuristic to generate a partition on the graph where nodes in the same partition are assigned the same output label in the improved segmentation. We will now discuss the three major components to our framework (graph creation, edge probabilities, and graph partitioning) in more detail.

\subsection{Graph Creation}
\label{sec:skeletonization}

%We generate nodes $N$ and edges $E$ to apply a graph-based optimization strategy for segmentation.
%In addition, these edges receive non-negative weights.

@@

\subsection{Edge Probabilities}

Our non-negative edge weights $w_e$ correspond to probabilities that two endpoints $e$ in $\mathbb{S}_c$ belong to the same neuron and should be merged. \hp{check} To compute these probabilities we train a 3D CNN classifier using the oversegmentation input volume and corresponding manually labeled ground truth data (Sec.~\ref{sec:dataset}).

>>>>

There are two types of errors that can occur in connectomics segmentation.
The first, called a split error, occurs when there are two segments that should have been merged. The second, called a merge error, happens when one segment should be split into two. Generally, it is much more difficult to correct merge errors than to correct split errors,
as the space of possible split proposals grow quickly~\cite{parag2015properties},.
Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. Our method takes as input over-segmentations of EM image volumes generated by state-of-the-art connectomics reconstruction pieplines (Sec.~\ref{sec:neuroproof}). Our goal is to identify locations of split errors and merge the corresponding segments automatically.

From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with non-negative edge weights $w_e$. The nodes correspond to label segments from the segmentation with edges between segments considered for merging. Ideally, our graph has edges corresponding to all of the segments that were erroneously split. To compute this graph we generate a skeleton for every segment in the pixel-based segmentation. The skeleton is a simplified representation of the overall shape of the neurons. From this skeleton we  identify potential merge locations and produce the corresponding edges for the graph. To find actual merges we run a classification CNN to generate edge weights that correspond to probabilites of merging. We then use a multicut heuristic to generate a partition on the graph where nodes in the same partition are assigned the same output label in the improved segmentation. We will now discuss the three major components to our framework (graph creation, edge weights assignment, and graph partitioning) in more detail.

\subsection{Graph Creation}
\label{sec:skeletonization}
\donglai{need some overview sentence}
%We generate nodes $N$ and edges $E$ to apply a graph-based optimization strategy for segmentation.
%In addition, these edges receive non-negative weights.

@@

\subsection{Edge Weights Assignment}
We aim to assign non-negative edge weights $w_e$, where adjacent nodes (endpoints $e$ in $\mathbb{S}_c$) connected with a big edge weight has higher chance to be merged to the same segment.
Instead of using handcrafted features to compute the similarity between adjacent nodes, we train a 3D CNN classifier to learn from the manually labeled oversegmentation input volume (Sec.~\ref{sec:dataset}).
%Our  edge weights  correspond to probabilities that two endpoints $e$ in $\mathbb{S}_c$ belong to the same neuron and should be merged. \hp{check}

### 2017-11-14 papers/cvpr2018/3_evaluation.tex
Donglai's rough pass on sec1-3

% !TEX root =  paper.tex
\section{Evaluation}

@@

\paragraph{\bf Kasthuri.}
The Kasthuri dataset consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. This dataset is $5342 \times 3618 \times 338$ voxels in size. The resolution of the dataset is $\SI[product-units=single]{3 x 3 x 30}{\nano\meter}^3$ per voxel. We evaluate our methods using the left cylinder of this 3-cylinder dataset. We downsample the dataset in the $x$ and $y$ dimensions to give a final resolution of $\SI[product-units=single]{6 x 6 x 30}{\nano\meter}^3$ per voxel. We divide the dataset into two volumes along the $x$ dimension where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$.

\paragraph{\bf FlyEM.}
The FlyEM dataset comes from the mushroom body of a 5-day old adult male Drosophila fly imaged by a focused ion-beam milling scanning electron microscopy. \hp{add ref} The mushroom body in this species is the major site of associative learning~\cite{takemura2017connectome}. The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume of which we use two cubes of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$. The resolution of this dataset is $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ or $1000$ voxels in each dimension in each of the two volumes.

@@

We evaluate the performance of the different methods using the split version of variance of information~\cite{meila2003comparing}. Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$.
Over and under-segmentation are quantified by the conditional entropy $H(GT | SG)$ and $H(SG | GT)$, respectively. Since we are measuring the entropy between two clusterings, better split variation of information scores are closer to the origin. The variation of information values of the original segmentation approaches at different stopping thresholds of agglomeration for both algorithms are shown in Fig.~\ref{fig:variation-of-information}. \hp{check}

@@

Table \ref{table:skeletonization} shows the overall success of our graph creation method with candidate pruning. \hp{not clear what this table is showing--explain. put this in the experiment section where you discuss the results}

>>>>

% !TEX root =  paper.tex
\section{Evaluation}
In this section, we describe the dataset, evaluation metric ...
\donglai{current organization is a bit unnatural.. too much details/overhead for the experiment setup, which can be put in the supplementary}

@@

\noindent\textbf{Kasthuri.}
The Kasthuri dataset consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. This dataset is $5342 \times 3618 \times 338$ voxels in size. The resolution of the dataset is $\SI[product-units=single]{3 x 3 x 30}{\nano\meter}^3$ per voxel. We evaluate our methods using the left cylinder of this 3-cylinder dataset. We downsample the dataset in the $x$ and $y$ dimensions to give a final resolution of $\SI[product-units=single]{6 x 6 x 30}{\nano\meter}^3$ per voxel. We divide the dataset into two volumes along the $x$ dimension where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$.

\noindent\textbf{FlyEM.}
The FlyEM dataset comes from the mushroom body of a 5-day old adult male Drosophila fly imaged by a focused ion-beam milling scanning electron microscopy. \hp{add ref} The mushroom body in this species is the major site of associative learning~\cite{takemura2017connectome}. The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume of which we use two cubes of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$. The resolution of this dataset is $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ or $1000$ voxels in each dimension in each of the two volumes.

@@

We evaluate the performance of the different methods using the split version of variance of information~\cite{meila2003comparing} (VI-s). Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$.
Over and under-segmentation are quantified by the conditional entropy $H(GT | SG)$ and $H(SG | GT)$, respectively. Since we are measuring the entropy between two clusterings, better VI-s scores are closer to the origin.
In Fig.~\ref{fig:variation-of-information}, we compute VI-s scores for the input over-segmentation result at different stopping thresholds of agglomeration.

@@

%Table \ref{table:skeletonization} shows the overall success of our graph creation method with candidate pruning. \hp{not clear what this table is showing--explain. put this in the experiment section where you discuss the results}

### 2017-11-14 papers/cvpr2018/paper.tex
Donglai's rough pass on sec1-3

\newcommand{\hp}[1]{\textcolor{red}{HP: #1}}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
Advancements in electron microscopy image acquisition have created massive connectomics datasets in the terabyte range that make manual reconstruction of neuronal structures infeasible. Current state-of-the-art automatic methods segment neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions. However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams. Instead, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways. Using the membrane labels of the pixel-based segmentation we first generate skeletons in 3D. Using this 3D graph we train automatic classifiers for shape description to detect impossible neural pathways by looking at geometric properties. We then apply efficient graph-based optimization strategies to improve the segmentation labels. We demonstrate the performance of our approach on multiple real-world connectomics datasets with average variation of information improvement of $X\times$. The paper provides insights into learning shape features for top-down graph-based neuron reconstruction.
\end{abstract}

%%%%%%%%	% BODY TEXT
\input{0_introduction}

>>>>

\newcommand{\hp}[1]{\textcolor{red}{HP: #1}}
\newcommand{\donglai}[1]{\textcolor{blue}{[Donglai: #1]}}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
Advancements in electron microscopy image acquisition hour have created massive connectomics datasets in the terabyte range that make manual reconstruction of neuronal structures infeasible. Current state-of-the-art automatic methods  segment neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions. However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams.

In this work, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways. 
Using the membrane labels of the pixel-based segmentation we first generate skeletons in 3D.
Using this 3D graph we train automatic classifiers for shape description to detect impossible neural pathways by looking at geometric properties. 
We then apply efficient graph-based optimization strategies to improve the segmentation labels. We demonstrate the performance of our approach on multiple real-world connectomics datasets with average variation of information improvement of $X\times$. 
%The paper provides insights into learning shape features for top-down graph-based neuron reconstruction.
\end{abstract}
%%%%%%%%	% BODY TEXT
\vspace{0.3in}

\input{0_introduction}
